Figure supplements

### 2022-08-22 text/Supplements.Rmd
delete some figures

![**Figure 4---figure supplement 1.** (A) Schematic diagram of the immunostaining procedure after calcium imaging. (B) The position of the cPRC (purple dashed line) in calcium imaging with GCaMP6s. Cells around the cPRC are numbered according to the position of the nuclei. (C) Immunostaining image using RGWamide (RGWa) and serotonin (Ser) antibodies (red) and DAPI (light blue) in the same region as (B). INRGW (green dashed line) and Ser-h1 (black arrowheads) identified from the numbered nuclear positions are shown. .](../figures/Fig4_sup1.png){width="100%"}

>>>>

![**Figure 4---figure supplement 1.** (A) An INNOS visualised by DAF-FM is shown (a white arrowhead). A black arrowhead indicates the position of the adult eye. The white dashed line indicates the outer frame of the larva. All subsequent images are of 2-day-old larvae. (B) Dual-colour imaging of DAF-FM (green) and RGECO1a (magenta) allows simultaneous visualisation of the INNOS and cPRCs. (C) Enlarged view of (B). cPRCs and INNOS are indicated by arrows.](../figures/Fig4_sup1.png){width="100%"}

![**Figure 4---figure supplement 2.** (A) Schematic diagram of the immunostaining procedure after calcium imaging. (B) The position of the cPRC (purple dashed line) in calcium imaging with GCaMP6s. Cells around the cPRC are numbered according to the position of the nuclei. (C) Immunostaining image using RGWamide (RGWa) and serotonin (Ser) antibodies (red) and DAPI (light blue) in the same region as (B). INRGW (green dashed line) and Ser-h1 (black arrowheads) identified from the numbered nuclear positions are shown.](../figures/Fig4_sup2.png){width="100%"}
